---
title: "Cleaning & Analysis Script"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Install and load pacman package
if (!require("pacman")) install.packages("pacman")

# Install and load required packages
p_load(rio, here, tidyverse, janitor) 
```

```{r import}
# Import data from saved DistillerSR reports
# Import preliminary data to build script (TODO: replace with final data when ready)
# Import the Effectiveness MA Eligibility data (file is already reconciled to one row per refid)
raw_MAeligibility_df <- import(here("data", "4dsw_effectiveness_eligibility_preliminary.xlsx"))

# Import Effectiveness Study Level data (file has one row per user, refid combo)
raw_study_df <- import(here("data", "4dsw_effectiveness_study_level_preliminary.xlsx"))

```

```{r functions}
#Write functions for formatting inline code
format_thousands <- function(x) {
  big_num <- format(x, big.mark = ",")
  return(big_num)
}

format_percent <- function(x, digits, force_decimal = FALSE) {
  if (force_decimal) {
    percentage <- paste0(format(round(x, digits), nsmall = digits), "%")
  } else {
    percentage <- paste0(round(x, digits), "%")
  }
  return(percentage)
}
```

# Cleaning

```{r clean}
# Transform MA eligibility data
td_MAeligibility <- raw_MAeligibility_df %>% 
  janitor::clean_names() %>% 
  select(-level)

# Transform study level data
td_study <- raw_study_df %>% 
  janitor::clean_names() %>% 
  distinct(across(-user), .keep_all = TRUE)

# Check there are no duplicate refIDs
sum(duplicated(td_study$refid))

```


# Descriptive Analyses

## Eligibility Assessment for Meta-Analysis

```{r eligibility}
# Number of studies ineligible due to no comparison
num_inelig_nocomp <- sum(td_MAeligibility$effectiveness_eligibility == "Ineligible due to no comparison group")

# Number of studies ineligible due to no student outcomes
num_inelig_outcome <- sum(td_MAeligibility$effectiveness_eligibility == "Ineligible on outcomes (no student outcomes)")

# Number of studies ineligible due critical ROB
num_inelig_rob <- sum(td_MAeligibility$effectiveness_eligibility == "Move to ROBINS-I eligibility assessment" & td_MAeligibility$robins_overall_judgment == "Critical")

num_elig <- sum(td_MAeligibility$robins_overall_judgment != "Critical" & !is.na(td_MAeligibility$robins_overall_judgment))

```

Out of the 111 studies that were included in the scoping review, only `r nrow(td_MAeligibility)` included information related to the effectiveness of implementing a four-day school week. From those `r nrow(td_MAeligibility)` studies, we excluded `r num_inelig_nocomp` studies that did not include a comparison group, `r num_inelig_outcome` studies that did not report on student outcomes, and `r num_inelig_rob` studies that we determined had critical risk of bias. Overall, we included `r num_elig` studies in this meta-analysis. 

## Study Characteristics



## Study Design

## Participants

## Settings

## Interventions

## Comparison

## OTHER RELEVANT FOR 4DSW?


# Meta-Analysis 
